---
title: "LinearModulewithPrediction"
author: "David"
date: "2023-10-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```



##Model 1

find an equation that expresses SIMS as a function of ARM

## Results

### Graphical Results

```{r}
plot(SIMS~ARM,data=data)
```

As arms strength increases, sims score increases.  There is a positive trend between arn strength and sim score.

### Numerical Results

```{r}
cor(data$SIMS, data$ARM)
```
This trend shows that we have a positive coloration of .68

### inference


```{r}
Model1 = lm(SIMS~ARM, data = data)
print(summary(Model1))
```



```{r}
plot(SIMS~ARM,data=data)
abline(Model1, col = "red")
```

for an increase of 1 in arm strength, sim score increases by 0.0545.


```{r}
newdata = data.frame(ARM = 88, GRIP = 94)
predict.lm(Model1, newdata, interval='prediction')
```




##Model 2

find an equation that expresses SIMS as a function of GRIP

## Results

### Graphical Results

```{r}
plot(SIMS~GRIP,data=data)
```

As grip strength increases, sims score increases.  There is a positive trend between grip strength and sim score.


### Numerical Results

```{r}
cor(data$SIMS, data$GRIP)
```
This trend shows that we have a positive coloration of 0.63


### inference




```{r}
plot(SIMS~GRIP,data=data)
abline(Model1, col = "blue")
```

for an increase of 1 in arm strength, sim score increases by 0.045.


##Model 3
find an equation that expresses SIMS as a function of ARM


## Results


### Graphical Results

There are no graphical results for model3 because i cant put to variables on one axis.


### Numerical results 

There are no numerical results since we have SIM as a function of two variables.

### inference

```{r}
Model3 = lm(SIMS~ARM, data = data)
print(summary(Model3))
```

```{r}
newdata = data.frame(ARM = 88, GRIP = 94)
predict.lm(Model3,newdata, interval='prediction')
```





